Exploring the structure of the bound proton with Deeply Virtual Compton Scattering

### 2019-02-28 eg6-letters/incoherent/incoherent_prl.tex
implement the recent comments from stepan

% DVCS selection
Incoherent DVCS events were selected by requiring an electron, a proton, and at 
least one photon in the final state. Electrons were identified as negatively 
charged tracks reconstructed in the drift chambers with an appropriate energy 
deposition in the electromagnetic calorimeter (EC) and a light yield above the 
threshold in the Cherenkov counters. The protons were identified from 
positively charged tracks based on their time-of-flight measured 
by the scintillator counters.  In addition, it was required that both the 
electron and the proton in the event originated from the same vertex at the 
target. The photons were detected in either the IC or the CLAS electromagnetic 
calorimeter. All the clusters within the IC fiducial region were assumed to be 
photons, while a timing cut was used to clean the EC photons from neutrons.  
Note that even though the DVCS reaction has only one real photon in the final 
state, events with more than one photon were not discarded at this stage. These 
extra photons were mostly soft photons from accidental coincidence which, as 
will be discussed below, the DVCS exclusivity cuts easily eliminated. In the 
following selection stage, the most energetic photon was considered as the DVCS 
photon candidate (see \cite{Hattawy:thesis} for additional details on the 
particle identification).

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. First, 
events were selected with $Q^{2}$ greater than 1 GeV$^2$ to ensure the 
applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
mass ($W=\sqrt{(q+p)^2}$, assuming that the initial proton is at rest) greater 
than 2 GeV to avoid the nucleon resonance region. The squared transferred 
momentum to the recoil proton $t$, calculated from the four-momentum vectors of 
the incoming and outgoing photons, was required to be greater than a minimum 
kinematically allowed value ($t_{min}$) at given $Q^2$ and $W$ defined as: 
\begin{equation}
t_{min} 
   =-Q^{2}~\frac{2(1-~x_{B})(1~-~\sqrt{1~+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}},
\end{equation}
where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
proton mass). We specifically used the kinematics of the photons to determine 
$t$ because the initial proton kinematics is unknown due to Fermi motion. We 
ensured the exclusivity of the incoherent DVCS events by imposing a series of 
constraints based on the four-momentum conservation in the reaction 
$ep\rightarrow e'p'\gamma$. These kinematical variables are: the coplanarity 
angle $\Delta\phi$ between the ($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) 
planes, the missing energy, mass, and transverse momentum of the $e'\gamma$ and 
$e'p'\gamma$ systems, the missing mass squared of the $e'p'$ system, and the 
angle $\theta$ between the measured photon and the missing momentum of the 
$e'p'$ system. The experimental data for the most relevant exclusivity 
variables are shown in Fig.~\ref{fig:kin-cuts}. Because of the Fermi motion of 
the nucleons in the helium nucleus, these cuts
are slightly wider than those previously used for free proton experiments~%
\cite{Girod:2007aa}. After the corrections discussed below, the asymmetries 
appear to be stable as a function of cut width and we saw no sizable effect 
that could be related to the initial momentum of the nucleons. We also rejected 
events where a $\pi^0$ was identified by the invariant mass of two photons. At 
the end of this selection process, about 30k events passed all the 
requirements; their kinematic distributions are shown in 
Fig.~\ref{fig:kin-coverage}.

>>>>

% DVCS selection
Incoherent DVCS events were selected by requiring an electron, a proton, and at 
least one photon in the final state using the standard particle identification 
Note that even though the DVCS reaction has only one real photon in the final 
state, events with more than one photon were not discarded at this stage. These 
extra photons were mostly soft photons from accidental coincidence which, as 
will be discussed below, the DVCS exclusivity cuts easily eliminated.  In the 
following selection stage, the most energetic photon was considered as the DVCS 
photon candidate.

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. 
First, events were selected with $Q^2$ grater than $1$ GeV$^2$ and the 
$\gamma^*p$ invariant mass ($W=\sqrt{(q+p)^2}$, assuming that the initial 
nucleon is at rest) greater than $2$ GeV. This is a commonly accepted region of 
kinematics used by the previous DVCS experiments to ensure the applicability of 
the DVCS handbag diagram and avoid the nucleon resonance region. The squared 
transferred momentum to the recoil proton $t$, calculated from the 
four-momentum vectors of the incoming and outgoing photons, was required to be 
greater than a minimum kinematically allowed value ($t_{min}$) at given $Q^2$ 
and $W$ defined as: \begin{equation}
t_{min} 
   =-Q^{2}~\frac{2(1-~x_{B})(1~-~\sqrt{1~+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}},
\end{equation}
where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
proton mass. This cut was applied to avoid accepting events in unphysical 
regions of kinematics due to the radiative effects. We specifically used the 
kinematics of the photons to determine $t$ because the initial proton 
kinematics is unknown due to Fermi motion.

In the final sample, the exclusivity of the incoherent DVCS events was ensured 
by imposing a series of constraints based on the four-momentum conservation in 
the reaction $ep\rightarrow e'p'\gamma$.  These kinematical variables are: the 
coplanarity angle $\Delta\phi$ between the ($\gamma,\gamma^*$) and 
($\gamma^*$,$p'$) planes, the missing energy, mass, and transverse momentum of 
the $e'\gamma$ and $e'p'\gamma$ systems, the missing mass squared of the $e'p'$ 
system, and the angle $\theta$ between the measured photon and the missing 
momentum of the $e'p'$ system. The experimental data for the most relevant 
exclusivity variables are shown in Fig.~\ref{fig:kin-cuts}.  Because of the 
Fermi motion of the nucleons in the helium nucleus, these cuts
are slightly wider than those previously used for free proton experiments~%
\cite{Girod:2007aa}. After the corrections discussed below, the asymmetries 
appear to be stable as a function of cut width and we saw no sizable effect 
that could be related to the initial momentum of the nucleons. We also rejected 
events where a $\pi^0$ was identified by the invariant mass of two photons. At 
the end of this selection process, about 30k events passed all the 
requirements; their kinematic distributions are shown in 
Fig.~\ref{fig:kin-coverage}.
